Documento Proyecto Mecánica Clásica
Ng

Editor mode.▾
    }

    \vspace{0.2cm}
        \rule{150mm}{0.5mm} %%%%----- -----%%%%
    \vspace{0.2cm}

    \section{Ejemplos}{

        \subsection{Tumores}

        \subsection{Osos-Salmones}
    
    }

    \vspace{0.2cm}
        \rule{150mm}{0.5mm} %%%%----- -----%%%%
    \vspace{0.2cm}

    \section{Conclusiones y Comentarios Finales}

    \vspace{0.2cm}
        \rule{150mm}{0.5mm} %%%%----- -----%%%%
    \vspace{0.2cm}

    \section{Apéndices}

    \vspace{0.2cm}
        \rule{150mm}{0.5mm} %%%%----- -----%%%%
    \vspace{0.2cm}

    \section{Bibliografías}

    \begin{enumerate}
        \item {

            \normalsize{Chemostat. (s.f.). Max Planck Institute For Marine Microbiology. Recuperado 21 de noviembre de 2024, de https://www.mpi-bremen.de/en/Chemostat.html}

        }

        \item {

            \normalsize{Monge-Nájera, J. (2002). Biología general. EUNED. ISBN 9789968311892. Consultado el 25 de noviembre de 2024.}
        
        }

        \item{
            \normalsize{Calvez, V., Lam, K.-Y. (2020) . Uniqueness of the viscosity solution of a constrained Hamilton–Jacobi equation. SPRINGER, 1-2. https://doi.org/10.1007/s00526-020-01819-0} 
        }

        \item {
            \normalsize{Barles, G., Perthame, B. (2007). Concentrations and constrained Hamilton-Jacobi equations arising in adaptive dynamics. Contemporary Mathematics, 439, 57-68.}
        }

        \item{
            \normalsize{Mirrahimi, S., Perthame, B., Bouin, E., Millien, P. (2011). Population formulation of adaptative meso-evolution: theory and numerics. The mathematics of Darwin’s legacy, 159-174.}
        }

        \item{
            \normalsize{De la Calleja, E. M., Carrillo, J. L., Santamaría-Holek, I. (2016). Bragg-Williams approximation for the dynamics of prey-predator biological associations. arXiv preprint arXiv:1603.03608.}
        }
    \end{enumerate}

\end{document}
